---
title: "READ ME"
author: "Tobias Castelberg"
date: "July 27, 2022"
output: pdf_document
---

# Optimistic CBS for Change Point Detection

This package provides code for fast and robust change point detection using circular
binary segmentation with reduced evaluations of the CUSUM statistic and its counterpart
for the L1 loss function.

### Installation from GitHub
Type `devtools::install_github("TobiasCastelberg/OCBS")` in the console to install
the package and load it as usual with `library(OCBS)`.

### Example on how to use the package

We provide an example on how to use the package with simulated data where we know the
true change points.

```{r data, include=TRUE}
set.seed(1)
X <- rep(c(0,6,0,-6,0),c(100,15,30,15,140)) + rt(300,2)
cps_true <- c(100,115,145,160)
plot(X)
abline(v=cps_true, lty=2)
```

We now estimate the change points using $L^1$ and $L^2$ optimization.

```{r cps, include=TRUE}
cpsL1 <- OCBS::optimisticCBS(X, optimization = "L1", method = "advanced")
cpsL2 <- OCBS::optimisticCBS(X, optimization = "L2", method = "advanced")
par(mfrow=c(1,2))
plot(X); title("L1 loss")
abline(v=cpsL1, col="red", lty=1, lwd=1.5)
abline(v=cps_true, lty=2, lwd=2)
plot(X); title("L2 loss")
abline(v=cpsL2, col="blue", lty=1, lwd=1.5)
abline(v=cps_true, lty=2, lwd=2)
```

The $L^2$ algorithm failed to find the anomalies. The noise structure
with $t_3$-distribution is too long tailed for the $L^2$ loss. We can improve 
the detection by removing outliers before using `optimisticCBS`.

```{r outlier removal}
Y <- OCBS::SmoothData(X)
plot(X, ylab = "Y in green")
points(which(X!=Y),Y[which(X!=Y)], col="green", pch=16)
points(which(X!=Y),X[which(X!=Y)], col="red")
```

Now that the outliers are removed, also the $L^2$ algorithm will find the change points. 

```{r cps without outliers}
cpsL1 <- OCBS::optimisticCBS(Y, optimization = "L1", method = "advanced")
cpsL2 <- OCBS::optimisticCBS(Y, optimization = "L2", method = "advanced")
par(mfrow=c(1,2))
plot(Y); title("L1 loss")
abline(v=cpsL1, col="red", lty=1, lwd=1.5)
abline(v=cps_true, lty=2, lwd=2)
plot(Y); title("L2 loss")
abline(v=cpsL2, col="blue", lty=1, lwd=1.5)
abline(v=cps_true, lty=2, lwd=2)
```


